\documentclass[11pt]{article}


\usepackage[a4paper]{geometry}


\title{BIT 2207:RESEARCH METHODOLOGY}
\author{ALVIN NSONGAMBI\\216004598\\16/u/10456PS}
\begin{document}
	\maketitle
	\pagenumbering{gobble}
\section{Fighting and stoping Alcoholism in uganda }
\paragraph{•}
This research focuses on finding the root cause of why Uganda is labeled the most alcoholic country in Africa and then trying to find possible solutions to the problem.
\paragraph{•}
Data will be collected such as names of alcohol brands and views of alcoholics will be gotten to determine which brands are more addictive as compared to others.
Information on why various people started drinking will also be complied to see which are thew biggest reasons people drink in Uganda and how each of there reasons can best be nullified so as the kill the problem of alcoholism in Uganda.
\paragraph{•}
Questions that will be asked in the data collection will includes the following.
\paragraph{•}
\textbf{What is your name?}

\textit{This information of name will be best used to determine based on research which tribe of people in Uganda are more alcoholic and likely to become alcoholics in the near future.Information based on last names can be used by ethnic experts interviewed to determine which tribe some one falls in.}


\textbf{How old are you?}

\textit{This information will be used to determine which age groups contains the most alcoholic people in the country }


\textbf{where are you from?}

\textit{This is to further help in the classification of which regions has more alcoholics in Uganda such that when implementing alcoholism solutions such regions are tackled first.
What is your favorite brand of alcohol?
This again is to find which brands are more likely to get someone to alcohol .images will be required so as to create a database to identify the brands by picture.
Considering some of these brands are not even well known and described on the Internet.}

\textbf{Why did you start drinking?}

\textit{Voice notes on people’s reasons for starting to drink will be found and so as to best understand and therefore implement a solution to the problem.
In what ways does alcohol affect you and your family?
Here people who are trying to get away from alcohol will be interviewed to determine further the effects of alcoholism.}


\textbf{Is it a manageable habit?}

\textit{An objective typed question to get in terms of number of Ugandans which people think alcoholism is a manageable habit.}


\textbf{What ways can one stop alcoholism?}

\textit{Solutions from the public will be compiled to best see how to eliminate or at least reduce on alcoholism in society.}

\end{document}