\documentclass[11pt]{article}


\usepackage[a4paper]{geometry}


\title{BIT 2207:RESEARCH METHODOLOGY}
\author{ALVIN NSONGAMBI\\216004598\\16/u/10456PS}
\begin{document}
	\maketitle
	\pagenumbering{gobble}
	\section{Finding free entertainment content online}
	\paragraph{}
	for years and years getting entertainment content for users especially those in third world countries has always been a challenge.
	\paragraph{}
	The entertainment content looked for is mainly free music ,movies , games and a lot of useful software that could infact usually be life changing
	and the only problem is buying legitmently online could cost as much as a teachers salary for a third world country.
	There fore I have reaserched a number methods and of sites that offer most of this entertainment content for free.
	\paragraph{}
	Finding free music
	\paragraph{}
	for song lovers in poor countries finding quality music of formats m4a, .flac and even good lossy .mp3 could be really frustrating considering most of the sites offer mp3 that has been compressed through several softwares and the loss in quality is devastating and for a luck of better words annoying.
	\paragraph{}
	Some sites even offer download links for the music which are not eye catching and usually the song titles and artist information put on one string.
	\paragraph{}
	Most of these dont even offer song art or instead put advertising song covers for example howwe.biz. Mdondomusic.com, mp3jaja.com(for which case it even puts a ka sound effect echoing the name of the site embedded within the song.
	Which is not nice.
	So today I offer you a better way for all song lovers to find good quality music free online.
	\paragraph{}
		Method I (spotify music)
	you are probably now thinking that spotify music does not work in african and most third generation countries.
	What if I tell you there is a way to actually unblock spotify and use this amazing app.
	And there is a way, simply by using a VPN.
	And yes most VPNs donont usually work very well in unblocking serious content. But there are some that I have personally found most useful.
	1.Turbo VPN
	its free of charge extremely fast and very simple to operate.
	I recommend this as an umber 1 choice.
	2.Droid VPN
	this may become tricky for some users as its both a tunnler and a VPN at the same time but once u get the hang of it. It becomes a very great tool and a person favorite of mine.
	Step2;
	Once you have your free vpn up and running you are good to create a spotify account ,doenload the spotify app and astart enjoying free quality m4a music.its a main streaming application and you will get free music as soon as it drops.
	You can also follow playlists and discover music that you might like online.
	Its by far the best steaming app in the world next to non.
	\paragraph{}
	Method 2;(YTD2)
	for those who might be complaining about spotify as it is data consuming and only works while online.
	There is an app called YTD2 developed by an indian guy to explicitly get you free music with good m4a format song art included and song information well documented.
	As you know this app violates a couple of online rules and there for is not available in play store.
	But you can download it through the following link.
	http:/theytd2.com
	
	\paragraph{}
	method3 (torrent sites).
	Torrents are a peer to peer sharing environment that enables people share content online without any restriction whatsoever.
	All you need to do is have a torrent downloader for example .bittorrent, utorent(apply to all platforms linux,windows and android) and my personal favorite for mobile phones flud torrent.
	Also worth pointing out that for ubuntu users it comes with transmission torrent which is light weight. The best in the bussiness.
	
	Now once you have your torrent downloader up and runing all you need to do is find a torrent site to get the music from.
	I recommend thepiratebay.org and rabg.com as the best for trucking down new releases of albums almost as soon as an album drops some lad some where I  the united states uploads the bought album mostly from itunes.
	And you never need to worry about these sites going away or being blocked as they have been around ages and seen many others fall or shift URLs without them even flinching.(there owners must be some next level hack stuff)/.
	Also you do not need a VPN as you are in a third world country with no aqctive internet law whatsoever.
	Free HD movies and series.
	Now lets talk about the love for free movies in high quality HD or even better, new emergging .mkv format.
	As discussed above torrent sites are gold and therefore can also be used to find good quality movies online.
	The only downside is there are high chances of downloading fake torents and low quality movies so you have to be care full and not just downloading anything.
	Usually looking at the number of people seeding on the torrent helps.
	The more people seeding it the higher thechances its not fake.
	Also know a few trusted uploaders(people that upload).
	You will have to find those by your self.
	\paragraph{}
	Method 2.
	as you have seen above torrents can be unrealiable when it comes to getting movies which brings us to our second method.
	Which is plain and simple. Trusted sites.
	I have made a list of a few trusted sites mainly
	toxicwap.com(good for series and movies).
	Tvshows4mobile.com(ideal fro series only. HD quality is admerable).
	There are others but I have found that if you know the above mentioned 2.
	you dont need to learn of any other sites as they are usually suficient.
	\paragraph{}
	Method 3.
	go to the google search bar and type index of series (followed by the title of the series or movie).
	Then click on the links the search results .
	This is the best way of finding .mkv file format videos which is remarkable quality.
	The disavantage is you might hit walls finding the right link.
	\paragraph{}
	Finding free games and software.
	\paragraph{}
	Well this you could google by title follwed by the word free download for eample free download PES 17 or search by cracked download PES 17.
	but then again you are likely to run into many links that wont work or lead you to a bunch of advertisement pages therefotre  iwouldnt recommend it.
	\paragraph{}
	The only way to get it nice and easy is yet again through torrent sites.
	Plain and simple its by far the best way to get free or cracked software.
	Or migrate to linux where 90% of things are free (just a suggestion not a recommendation).
	
	
	\newpage
\end{document}